Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-12-07 Ben_Manuscripts/structure_paper/Draft.tex
More edits

  While the Col\textsubscript{h} phase is described as dry, it is 
  %MRS3: ``possible'' -> likely, and give some explanations why we think
  %likely? 
  likely that small amounts of ambient water may be leached into the system. The
  hydrogen bonding network formed by the water may play a role in structuring the
  pore.  We can use simulated X-ray diffraction patterns to see if there is any
  meaningful structural difference between a "dry" and "wet" system

@@

  In this study, we build a significantly more realistic atomistic model of LLC membranes
  than has ever previously been done, and explore what new structural information can be gained
  and what structure hypotheses are supported by this model.

  \begin{itemize}
    \item We validate the model using as much experimental information as possible.
    \item We are most interested in reproducing the conclusions about structure
    which have been made from X-ray diffraction (XRD) experiments and in matching ionic
    conductivity measurements~\cite{feng_thin_2016}.
  \end{itemize}

  We used experimental wide angle X-ray scattering (WAXS) data (produced as described
  in~\cite{feng_scalable_2014}) and small angle X-ray scattering (SAXS) data from~\cite{feng_thin_2016}
  to inform our choices of some initial structural parameters (Figure~\ref{fig:SWAXS}). We rely primarily
  on the 2D WAXS data since it encodes all structural details down to the sub-nm scale.
  \begin{itemize}
        \item There are five major features of interest present in the 2D experimental
        pattern shown in Figure~\ref{fig:WAXS}.
        \item The first is located at $q_z$ = 1.7 \angstrom$^{-1}$,
        corresponding to a real spacing of 3.7 \angstrom~. The reflection is
        attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
        perpendicular to the membrane plane, or z-axis \cite{feng_scalable_2014}. For simplicity, this
        reflection will be referred to as R-$\pi$.
        \item A weak intensity line is located at exactly half the $q_z$ value of
        R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a
        real space periodic spacing of 7.4 \angstrom~. This reflection has been
        interpreted  as 2\textsubscript{1} helical ordering of aromatic rings
        along the z axis meaning if the positions of the aromatic rings can
        be traced by a helix, then for each turn in the helix, there should be
        two aromatic rings. For this reason it will be referred to as R-helix.
        \item A third major reflection is marked by a low intensity ring located
        at r = 1.4 \angstrom$^-1$. The real space separation
        corresponds to 4.5 \angstrom~ which is characteristic of the average
        spacing between packed alkane chains. This reflection will be called R-alkanes.
        \item Within R-alkanes, are four spots of higher relative intensity which
        will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
        in their respective quadrants. In many liquid crystal systems this can be
        explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: References
        \item The final feature corresponds to the spacing and symmetry of
        the d\textsubscript{100} plane which can be related to the distance between
        pores. The feature, which will be called R-pores, is characterized by dots
        along $q_z$ = 0. The spacing between dots is indicative of the hexagonal
        symmetry of the packed pores. The same information at higher resolution is obtained using a SAXS
        setup. By radially integrating the 2D data one gets a 1D curve which is
        shown in Figure~\ref{fig:SAXS}.  % BJC: I also have 2D SAXS data
  \end{itemize}

@@

%    \begin{itemize}
%            \item We have compared simulated X-ray diffraction patterns to experiment in
%            order to match major features present in the 2D patterns.
%            \item We calculated ionic conductivity using two agreeing methods.
%            \item We examined the the influence of crosslinking on membrane structure.
%    \end{itemize}
%    \item The structure-building approach and analysis used in this paper can be readily extended
%    to the H\textsubscript{II} phase, other similar LC systems and ultimately to help design
%    real membranes.
%  \end{itemize}

>>>>

  While the Col\textsubscript{h} phase is described as dry, it is has been
  suggested by experimentalists in unpublished communications that it is likely
  that small amounts of ambient water are leached into neat monomer.
  Experimentally, achieving a hexagonal phase with a completely dry system has
  proven difficult. If neat monomer is allowed to sit in ambient conditions, its
  color turns from transparent to slightly opaque and a hexagonal phase forms.
  Although we will not explore whether water is necessary for self assembly, we
  hypothesize that the hydrogen bonding network formed by the water may play a
  role in structuring the pores and holding together the hexagonal phase. We can
  use simulated X-ray diffraction patterns to see if there is any meaningful
  structural difference between a "dry" and "wet" system.

@@

  In this study, we build a significantly more realistic atomistic model of LLC
  membranes than, to our knowledge, has ever previously been done, and explore
  what new structural information can be gained and what structure hypotheses are
  supported by this model. We validate the model using as much experimental
  information as possible. We are most interested in reproducing the conclusions
  about structure which have been drawn from X-ray diffraction (XRD) experiments
  and in matching ionic conductivity measurements \cite{feng_thin_2016}.

  %BJC: Would it be better to describe each reflection as a numbered list (like with the questions above?)
  We used experimental wide angle X-ray scattering (WAXS) data (produced as 
  described in \cite{feng_scalable_2014}) and small-angle X-ray scattering (SAXS)
  data from \cite{feng_thin_2016} to inform our choices of some initial
  structural parameters (Figure~\ref{fig:SWAXS}). We rely primarily on the 2D
  WAXS data since it encodes all structural details down to the sub-nm scale.
  There are five major features of interest present in the 2D experimental
  pattern shown in Figure \ref{fig:WAXS}. The first is located at $q_z$ = 1.7
  \angstrom$^{-1}$, corresponding to a real space separation of 3.7 \angstrom~.
  The reflection is attributed to $\pi$-$\pi$ stacking between aromatic rings in
  the direction perpendicular to the membrane plane, or z-axis
  \cite{feng_scalable_2014}. For simplicity, this reflection will be referred to
  as R-$\pi$. A weak intensity line is located at exactly half the $q_z$ value of
  R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a real space periodic
  spacing of 7.4 \angstrom~. This reflection has been interpreted as
  2\textsubscript{1} helical ordering of aromatic rings along the z axis meaning
  if the positions of the aromatic rings can be traced by a helix, then for each
  turn in the helix, there should be two aromatic rings. For this reason it will
  be referred to as R-helix. A third major reflection is marked by a low
  intensity ring located at r = 1.4 \angstrom$^-1$. The real space separation
  corresponds to 4.5 \angstrom~ which is characteristic of the average spacing
  between packed alkane chains. This reflection will be called R-alkanes. Within
  R-alkanes, are four spots of higher relative intensity which will be called
  R-spots. All are located $\approx 40$ degrees from the $q_z$ axis in their
  respective quadrants. In many liquid crystal systems this can be explained by
  the tilt angle of the alkane chains with respect to the xy plane.  The final
  feature corresponds to the spacing and symmetry of the d\textsubscript{100}
  plane which can be related to the distance between pores.  The feature, which
  will be called R-pores, is characterized by dots along $q_z$ = 0. The spacing
  between dots is indicative of the hexagonal symmetry of the packed pores. The
  same information at higher resolution is obtained using a SAXS setup. By
  radially integrating the 2D data one gets a 1D curve which is shown in
  Figure~\ref{fig:SAXS}.

@@
